\documentclass[letterpaper, notitlepage, 12pt]{article} %letterpaper: paper size; npt: the size of letters

\usepackage{color} %contains switches for color
\usepackage[margin=2cm]{geometry}%margin: the margin of the up, bottom, left, right of the page

\begin{document}
\title{The First Article I Made through LaTeX}%The title of the article
\author{Meihui Liu}%The author of the article
%\date{October 3030}
\date{\today}%The date you wrote the article
\maketitle

\begin{abstract}
Some random text from http://randomtextgenerator.com/:
Rooms oh fully taken by worse do. Points afraid but may end law lasted. Was out laughter raptures returned outweigh. Luckily cheered colonel me do we attacks on highest enabled. Tried law yet style child. Bore of true of no be deal. Frequently sufficient in be unaffected. The furnished she concluded depending procuring concealed. 

Blind would equal while oh mr do style. Lain led and fact none. One preferred sportsmen resolving the happiness continued. High at of in loud rich true. Oh conveying do immediate acuteness in he. Equally welcome her set nothing has gravity whether parties. Fertile suppose shyness mr up pointed in staying on respect. 
\end{abstract}

\section{Introduction}

\subsection{Number 1}
Hello {\color{red} World} again!

\subsection{Number 2}
Some random text from http://randomtextgenerator.com/:
Considered an invitation do introduced sufficient understood instrument it. Of decisively friendship in as collecting at. No affixed be husband ye females brother garrets proceed. Least child who seven happy yet balls young. Discovery sweetness principle discourse shameless bed one excellent. Sentiments of surrounded friendship dispatched connection is he. Me or produce besides hastily up as pleased. Bore less when had and john shed hope. 

\newpage
This's three words \break Try it.

This's three words \hfil\break Try it.

This's three words \\ Try it.

Conveying or northward offending admitting perfectly my. Colonel gravity get thought fat smiling add but. Wonder twenty hunted and put income set desire expect. Am cottage calling my is mistake cousins talking up. Interested especially do impression he unpleasant travelling excellence. All few our knew time done draw ask. 

Supported neglected met she therefore unwilling discovery remainder. Way sentiments two indulgence uncommonly own. Diminution to frequently sentiments he connection continuing indulgence. An my exquisite conveying up defective. Shameless see the tolerably how continued. She enable men twenty elinor points appear. Whose merry ten yet was men seven ought balls. 
\end{document}